%-------------------------
% Resume in Latex
% Author : Caleb Chan
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[british]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{center}
    \textbf{\Huge \scshape Caleb Chan} \\ \vspace{1pt}
    \small +44 7887 379330 $|$ \href{mailto:calebchanwy@gmail.com}{\underline{calebchanwy@gmail.com}} $|$
    \href{https://linkedin.com/in/calebchanwy}{\underline{linkedin.com/in/calebchanwy}} $|$
    \href{https://github.com/calebchanwy}{\underline{github.com/calebchanwy}}
\end{center}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Engineer - DevOps}{2024 - 2026}
      {Ciena Corporation}{London, UK}
      \resumeItemListStart
        \resumeItem{Provided essential tools and services that developers rely on for creating quality and on-time software releases to customers of Vyatta NOS and SAOS}
        \resumeItem{Administered 20+ Linux based systems, implementing disaster recovery plans, automated backups, user access control and regular maintenance to improve service resilience.}
        \resumeItem{Successfully migrated 10+ critical services, from XCP-NG to Proxmox, with Ansible scripts for automated provisioning, configuration and Infrastructure-as-Code redeployment, limiting downtime.}
        \resumeItem{Delivered a containerized developer environment using Bash, Python, and Ansible, enabling platform-independent access to tool sets and SDKs which was adopted as the default workflow for 30+ Vyatta developers.}
        \resumeItem{Developed a Grafana based monitoring application with 10+ live dashboards to visualise DORA metrics, build KPIs, Bitbucket PR activity and infrastructure health using Zabbix integrations, giving transparency for engineers and senior management.}
        \resumeItem{Constant collaboration between developer and product testing teams across 3 international sites and time zones, participating in vital knowledge sharing, expediting company software production and objectives.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Engineer Intern}{2021} %
      {VoucherCodes}{London, UK} %
      \resumeItemListStart
        \resumeItem{Redesigned and migrated web pages to a new front-end stack built on Tailwind.}
        \resumeItem{Used Tableau to query large datasets, providing and presenting reports on click statistics and conversion rates.}
      \resumeItemListEnd

    \resumeSubheading
      {Audio \& Visual Team Leader - Volunteer}{2019 -- Present}
      {True Jesus Church}{London, UK}
      \resumeItemListStart
        \resumeItem{Leading meetings, training sessions and allocating jobs for team members for effective team collaboration.}
        \resumeItem{A.V. systems and infrastructure management, including Control4 and Ubiquiti networking hardware, helping facilitate weekly services and special events.}
        \resumeItem{Regular updating of local church websites, built on WordPress, to keep church members informed and engage members of the public online.}
        \resumeItem{Owner and maintainer of a VB.NET program that displays live information for in-person attendees. Dealing with constant user feedback and iterative updates to meet demands. Adopted in several locations in the UK.}
      \resumeItemListEnd
      
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
        \resumeProjectHeading
          {\textbf{Educational Integrated Devloper Environment} $|$ \emph{Vue.JS, Typescript}}{}
          \resumeItemListStart
            \resumeItem{Designed and created a novel inbuilt tutorial system into Strype, aimed to improve the onboarding experience for novice programmers using Strype.}
            \resumeItem{Produced an extensive dissertation styled report, documenting the complete development lifecycle and evaluation of the new feature, helping academics understand the background, design decisions and motivations for inbuilt tutorial systems.}
          \resumeItemListEnd

        \resumeProjectHeading
          {\textbf{Gamified Digital Journaling App} $|$ \emph{Django, Tailwind, Git, CI/CD}}{}
          \resumeItemListStart
            \resumeItem{Led and participated in the development of a gamified digital journaling app aimed at getting more young adults into daily journaling through streaks, trophies and points.}
            \resumeItem{Gained hands-on experience with Django, Tailwind and fundamental SDLC best practices, including agile, Git, code reviews, CI/CD pipelines and automated unit testing.}
          \resumeItemListEnd

        \resumeProjectHeading
            {\textbf{ML Exercise Tracker} $|$ \emph{Java, Azure SQL, Machine Learning Kit}}{}
            \resumeItemListStart
                \resumeItem{Delivered a Java Android app that used Google's Machine Learning Kit to track and detect motion-based workouts using a device's camera feed.}
                \resumeItem{Enabled online user competition by hosting a remote database on Azure, saving exercise data remotely.}
                \resumeItem{Implemented user protection and privacy through authenticated SQL queries and secure database management.}
            \resumeItemListEnd
            
        \resumeProjectHeading
            {\textbf{COVID-19 Data Tracker} $|$ \emph{Java, Java.FX}}{}
            \resumeItemListStart
                \resumeItem{Created a Java.FX GUI presenting COVID-19 data taken from all London boroughs, to help local boroughs visualize and interact with data during a selected time period.}
            \resumeItemListEnd

    \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {King's College London}{London, UK}
      {Bachelor of Science (Hons), Computer Science With A Year In Industry}{2022 -- 2026}
      \resumeItemListStart
        \resumeItem{Current final year student. Average for Year 2: 82\% (on track for first-class honours).}
      \resumeItemListEnd
    \resumeSubheading
      {Woodhouse College}{London, UK}
      {Advanced Level Qualifications (A-Levels)}{2020 -- 2022}
      \resumeItemListStart
        \resumeItem{A*, A*, A*, A* in Computer Science, Further Mathematics, Mathematics and Physics.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

  
%-----------PROGRAMMING SKILLS-----------
\section{Technical \& Other Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming Languages}{: Ansible, Bash, C++, Python, Java, VB.NET, Scala} \\ %
     \textbf{Software Tools}{: Atlassian, Docker, Git, Grafana, Proxmox, Linux, Zabbix} \\ %
     \textbf{Languages}{: Fluent in English and Cantonese} \\ %
     \textbf{Awards \& Extracurriculars}{: Competed in the 2022 Reply Code Challenge (Teen Edition) and was placed in the top 20 UK teams. Instruments: Piano (Grade 8) \& Violin (Grade 2). Jack Petchey's Speak Out Assembly Finalist.}
    }}
 \end{itemize}

%-------------------------------------------
\end{document}